
Let's try and find the indentity of the clusters below



```{r}
library(Seurat)
library(dplyr)
data("pbmc_small")

pbmc_small@ident
TSNEPlot(pbmc_small, do.label = T)

```



First, let's detect the markers.

```{r}
pbmc_markers <- Seurat::FindAllMarkers(pbmc_small)

```

So these are the markers for the different clusters. Let's run wcit and see if we can infer which type of cells they are most similar to. 

```{r}
library(wcit)
for (i in levels(pbmc_markers$cluster)){
  print(paste('For cluster', i, 'The most likely cell types are:'))
  wcit(pbmc_markers$gene[pbmc_markers$cluster == i])
}
```

Let's manually look at the markers, as it is done normally.

```{r}
for (i in levels(pbmc_markers$cluster)){
  print(pbmc_markers$gene[pbmc_markers$cluster == i][1:10])
}
```

Cluster 0 has a higher expression of CD3D, which points at it being enriched for T cells, indeed. 
Cluster 1  expresses CD14, Lysozime and S100A9, pointing at monocytes/dendritic cells.
Cluster 2 expresses GNLY, GZMB, PRF1,GZMA and NKG7, pointing at likely being a cluster of cytotoxic cells.
Cluster 3 expresses PPBP, a classic platelet marker, corroborating its nature as megakaryocites/platelets.
